The Calculus of Linear Constructions

### 2022-01-20 writing/draft7/draft7.tex
draft

Over the years, work has been done to enrich linear type theories with dependent types. Cervesato and Pfenning extend the Edinburgh Logical Framework with linear types \cite{lf,llf}, being the first to demonstrate that dependent types and linear types can coexist within a type theory. V\'{a}k\'{a}r \cite{vakar14} presents a linear dependent type theory, with syntax and semantics drawing inspiration from DILL \cite{dill}. Krishnaswami et al. present a dependent linear type theory LNL$_D$ \cite{neel15} based on Benton's earlier work on mixed linear and non-linear calculus. The inclusion of universe sorts in CLC draws inspiration from LNL$_D$, they however, differ in their usage. LNL$_D$ uses two typing judgments for linear and non-linear types and two adjoint connectives to mediate between these two judgments, CLC uses a single typing judgment without any mediating connectives. Based on initial ideas of McBride \cite{nothing}, Atkey's Quantitative Type Theory (QTT) \cite{qtt} uses semi-ring annotations to track variable occurrence, simulating irrelevance and linear and affine types within a unified framework.

>>>>

Over the years, work has been done to enrich linear type theories with dependent types. Cervesato and Pfenning extend the Edinburgh Logical Framework with linear types \cite{lf,llf}, being the first to demonstrate that dependent types and linear types can coexist within a type theory. V\'{a}k\'{a}r \cite{vakar14} presents a linear dependent type theory, with syntax and semantics drawing inspiration from DILL \cite{dill}. Krishnaswami et al. present a dependent linear type theory LNL$_D$ \cite{neel15} based on Benton's earlier work on mixed linear and non-linear calculus. The inclusion of universe sorts in CLC takes inspiration from LNL$_D$ but the two theories differ in overall design. LNL$_D$ uses two typing judgments for linear and non-linear types and two adjoint connectives to mediate between these two judgments whereas CLC uses a single typing judgment without any mediating connectives. Based on initial ideas of McBride \cite{nothing}, Atkey's Quantitative Type Theory (QTT) \cite{qtt} uses semi-ring annotations to track variable occurrence, simulating irrelevance and linear and affine types within a unified framework.
